---
title: "A. Set Theory: Set Operations"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-D"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
  showDetails: false
---

## Concept Overview

* Union ($A \cup B$)
* Intersection ($A\cap B$)
* Difference ($A-B$)
* Universal set (U or S)
* Complement ($A^c = U-A$)

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

showDetails <- isTRUE(params$showDetails)
hideText <- function(text, show=showDetails){
  if(show) text else
    funs2teach::hideText(text, docType = 'html')
}

options(knitr.kable.NA = '')
set.seed(123)
```

## Union $\cup$
- Any elements of two (or more) sets
- $A\cup B = \{ x | x\in A \text{ OR } x\in B\}$

- Example:
  - $A = \{1, 2, 3\}, B = \{3, 4, 5\}$

  - $A \cup B =$ `r hideText('{1, 2, 3, 4, 5}')`
   
## Intersection $\cap$
- Common elements of two (or more) sets
- $A\cap B = \{ x | x\in A \text{ AND } x\in B\}$

- Example:
  - $A = \{1, 2, 3\}, B = \{3, 4, 5\}$

   * $A \cap B =$ `r hideText('{3}')` 

## Q1.
What happens to the cardinality of union and intersection?

:::{.nonincremental}

a. There will be no difference.
b. Cardinality of *union* and *intersection* goes up.
c. Cardinality may increase for *union* but may decrease for *intesection*. 
d. Cardinality will increase for *union* and decrease for *intesection*. 

:::

## Differnce $A\setminus B$ or $A-B$
- Elements in $A$ that are not in $B$
- $A-B = A\setminus B= \{ x | x\in A \text{ BUT (AND) } x\notin B\}$

- Example:
  - $A = \{1, 2, 3\}, B = \{3, 4, 5\}$
   * $A - B =$ `r hideText('{1, 2}')`

## Universal Set and Complement
- Universal Set $U$: All relevant elements
- Complement of Set $A$: Difference of Universal and set $A$
  - $A^c=A'=U-A$

- Example:
  - $U=\{1, 2, ..., 6\}, A = \{1, 2, 3\}$
  - $A^c$ = Complement of A = `r hideText('{4, 5, 6}')`
  
## Practice Problems
:::{.nonincremental}

1. Let $X = \{a, b, c\}, Y = \{b, c, d\}$

    * Find X $\cup$ Y.
    
    * Find X $\cap$ Y.
    
    * $n(X\cup Y) =$ 
   
2. Find the complement of $A = \{1, 2\}$ in universal set $U = \{1, 2, 3, 4\}$

\

3. Suggest an equivalent set for $A = \{1, 2\}$.

:::

## Q2.
What is $A \cap B$ if $A = \{2, 4, 6\}$ and $B = \{1, 2, 3\}$?

:::{.nonincremental}

A) {1, 2, 3, 4, 6}
B) {2}
C) ∅
D) {4, 6}

:::

## Q3.
If $U = \{1,2,3,4,5\}$ and $A = \{2,4\}$, what is the complement of $A$?

:::{.nonincremental}

A) {1,3,5}
B) {2,4}
C) ∅
D) {1,2,3,4,5}

:::

