---
title: "A. Set Theory: Venn Diagram"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-E"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
  showDetails: false
---

### Topics
* **Venn diagrams** 
* **subsets** as **events**

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

showDetails <- isTRUE(params$showDetails)
hideText <- function(text, show=showDetails){
  if(show) text else
    funs2teach::hideText(text, docType = 'html')
}

options(knitr.kable.NA = '')
set.seed(123)
```

## Venn Diagram
- Representing 
  - Universal Set as a box
  - Subsets as segments of the box (circles)

:::{.fragment}

```{r, echo=FALSE}
#| fig-width: 8
#| fig-height: 3
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U');
funs2teach::drawPolygon(
    n=1000, r=4, center=c(-1.5, 0), angle=pi, 
    labels = 'A', add=TRUE, col=adjustcolor('blue', .5));
funs2teach::drawPolygon(
    n=1000, r=4, center=c(1.5, 0), 
    labels = 'B', add=TRUE, col=adjustcolor('red', .5));

```

:::

## Guided Example 1
- **Set A**: students who take math. **Set B**: students who take English.

::: {.columns}
::: {.column}
  * 12 in both A and B
:::
::: {.column}
  * 18 only in A
:::
:::
<!-- end columns -->

  * 10 only in B
  * Fill a Venn diagram and answer: How many are in A ∪ B?

:::{.fragment}
```{r, echo=FALSE}
#| fig-width: 8
#| fig-height: 3
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U');
funs2teach::drawPolygon(
    n=1000, r=4, center=c(-1.5, 0), angle=pi, 
    labels = 'A', add=TRUE, col=adjustcolor('blue', .5));
funs2teach::drawPolygon(
    n=1000, r=4, center=c(1.5, 0), 
    labels = 'B', add=TRUE, col=adjustcolor('red', .5));
```

:::


## Guided Example 2
- Universal set has 50 students. 35 take math, 20 take science, 10 take both. many students take neither?
  * Math only = 25, Science only = 10, Both = 10
  * Total in sets = 25 + 10 + 10 = 45
   
   `r hideText('**Answer: 50 – 45 = 5**')`

:::{.fragment}
```{r, echo=FALSE}
#| fig-width: 8
#| fig-height: 3
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U');
funs2teach::drawPolygon(
    n=1000, r=4, center=c(-1.5, 0), angle=pi, 
    labels = 'A', add=TRUE, col=adjustcolor('blue', .5));
funs2teach::drawPolygon(
    n=1000, r=4, center=c(1.5, 0), 
    labels = 'B', add=TRUE, col=adjustcolor('red', .5));

```
:::

## Practice Problems
1. In a class of 40, 28 like coffee, 22 like tea, 15 like both.
  * How many like only coffee?

2. 100 students: 70 use Instagram, 50 use TikTok, 30 use both.
  * How many use neither?


## Q1.
:::{.nonincremental}
- In a survey of 60 people, 35 like chocolate, 30 like vanilla, 10 like both. How many like only chocolate?

A) 25
B) 35
C) 10
D) 45
:::

## Q2
:::{.nonincremental}

- If 10 students play guitar, 6 play piano, and 4 play both, how many play only one instrument?

A) 6
B) 8
C) 16
D) 4
:::

## Concept Overview
* **Venn diagrams** represents sets and their relationship by (overlapping) circles.
  * A set is also called an **event**.
* Common regions in a Venn Diagram with two sets:
  * **Only A**: in A but not B
  * **Only B**: in B but not A
  * **A $\cap$ B**: in both A and B
  * **A $\cup$ B**: in A or B or both
* Cardinal Number of a Union of two sets
    * $n(A∪B)=n(A)+n(B)−n(A\cap B)$
    * $n(A∪B)=n(A-B)+n(B-A)+n(A\cap B)$
