---
title: "A. Set Theory: Application of Venn Diagram"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-F"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
  showDetails: false
---

## Concept Overview
Venn diagrams can help us in real-world problems with:

* Categorizing overlapping groups
* Finding a set cardinality
* Understanding surveys

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

showDetails <- isTRUE(params$showDetails)
hideText <- function(text, show=showDetails){
  if(show) text else
    funs2teach::hideText(text, docType = 'html')
}

options(knitr.kable.NA = '')
set.seed(123)
```

## Guided Example 1
:::{.nonincremental style="font-size: 0.85em"}
::: {.columns}
::: {.column}
- In a gym of 80 members: 45 do yoga, 35 do weights, 20 do both
* How many do neither?
  + At least one: `r hideText('45 + 35 – 20 = 60')`
  + **Doing neither:** `r hideText('80 – 60 = 20')` 
:::
::: {.column}
```{r, echo=FALSE}
#| fig-width: 5
#| fig-height: 5
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U')
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=c(-1.5, 0), col=adjustcolor('blue', .5),
    border = 'blue', 
    labels = 'Y', angle=pi, cex = 1.5, adj=1, 
    add=TRUE)
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=c(1.5, 0), col=adjustcolor('red', .5), 
    labels = 'W', angle=0, cex = 1.5, adj=1,
    border = 'red', 
    add=TRUE)
```
:::
:::
<!-- end columns -->

:::


## Guided Example 2
:::{.nonincremental style="font-size: 0.85em"}
In a college:

::: {.columns}
::: {.column}
* 120 students study Spanish, 90 French, 40 both
* How many study only one language?
   + Spanish only =  `r hideText('120 - 40 = 80')`, French only =   `r hideText('90 - 40 = 50')` 
   + **Total for one language =** <br/> `r hideText('80 + 50 = 130')`
:::
::: {.column}
```{r, echo=FALSE}
#| fig-width: 5
#| fig-height: 5
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U')
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=c(-1.5, 0), col=adjustcolor('blue', .5),
    border = 'blue', 
    labels = 'S', angle=pi, cex = 1.5, adj=1, 
    add=TRUE)
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=c(1.5, 0), col=adjustcolor('red', .5), 
    labels = 'F', angle=0, cex = 1.5, adj=1,
    border = 'red', 
    add=TRUE)
```
:::
:::
<!-- end columns -->
:::

## Practice Problems
:::{.nonincremental style="font-size: 0.85em"}

1. Of 100 voters: 60 support candidate A, 50 support B, 20 support both.
   * How many support only A or only B?

\

2. 40 employees have pets: 25 have dogs, 18 have cats, 10 have both.
   * How many have only one pet?
   
\

:::

## Problems with Three Sets
:::{.nonincremental style="font-size: 0.85em"}
::: {.columns}
::: {.column}
In a survey of 100 college students, it was found that in high school, 25 took Physics, 45 took Biology, 48 took Math, 10 took Physics and Math, 8 took Biology and Math, 6 took Physics and Biology, and 5 took all three subjects.

a) Fill in all eight regions of the Venn diagram.
b) How many did not take any of the three subjects? 
:::
::: {.column}
c) How many took biology, but not Math?
```{r, echo=FALSE}
#| fig-width: 5
#| fig-height: 5
par(mar=c(0,0,0,0), xpd=TRUE)
funs2teach::drawPolygon(
    n=4, r=10, angle=pi/4, labels = 'U')
d <- 2.5
dth <- 2*pi/3*(0:2)
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=d*c(cos(dth[1]), sin(dth[1])),
    col=adjustcolor('blue', .5),
    border = 'blue', 
    labels = 'P', angle=dth[1], cex = 1.5, adj=1, 
    add=TRUE)
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=d*c(cos(dth[2]), sin(dth[2])),
    col=adjustcolor('yellow', .5),
    border = 'yellow', 
    labels = 'M', angle=dth[2], cex = 1.5, adj=1, 
    add=TRUE)
funs2teach::drawPolygon(
    n=1000, r=4, 
    center=d*c(cos(dth[3]), sin(dth[3])),
    col=adjustcolor('red', .5), 
    labels = 'B', angle=dth[3], cex = 1.5, adj=1,
    border = 'red', 
    add=TRUE)
```
:::
:::
<!-- end columns -->
:::

## Quiz: Q1
:::{.nonincremental}

- In a group of 90 students, 50 play soccer, 40 play basketball, and 20 play both. How many play at least one of the sports?

A) 70
B) 50
C) 30
D) 90

:::

## Quiz: Q2
:::{.nonincremental}

- In a study of 200 people, 120 liked comedy movies, 90 liked action, and 50 liked both. How many liked none of them?

A) 160
B) 80
C) 40
D) 10
:::
