---
title: "A. Set Theory: Set Notations"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-C"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
  showDetails: false
---

## Topics:
- Set Definition Notations
- Set Membership Notations
- Cardinality of a Set
- Set Subset Notations
- Equality & Equivalancy

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

showDetails <- isTRUE(params$showDetails)
hideText <- function(text, show=showDetails){
  if(show) text else
    funs2teach::hideText(text, docType = 'html')
}

options(knitr.kable.NA = '')
set.seed(123)
```

## Sets & Definition Notations

* Naming Convention: Capital Letters
* Definition:
  * Descriptive Notation
    - $A$ is the set of integer numbers between 1 and 9, inclusive.

  * Roster Notation
    - $A=\{1, 2, ..., 9\}$

  * Set-builder Notation
    - $A=\{x: x\text{ is integer}, 1\le x \le 9\}$
    - $A=\{x| x\in \mathbb{Z}, 1\le x \le9\}$

## Elements & Membership Notation
* Naming Convention: Lower-case Letters
* Membership:
  - `Member of` (Symbols: $\in$)
    - $1 \in \{1, 2, 3, ..., 9\}$
  - `not a member of` (symbol $\notin$)
    - $1.5 \notin \{1, 2, 3, ..., 9\}$
* Cardinality of Set $A$ (symbol:$n(A)$):
  * Number of elements in $A$: $n(A)=9$
    
## Subset Notation
* Subset (Symbol $\subseteq$)
  * $A\subseteq B$ means all members of $A$ are in $B$.
  * $A$ could be equal to $B$, in this difinition.

* Proper Subset (Symbol $\subset$)
  * $A\subset B$ but $A\ne B$
    * $B$ has at least one more element.

* Emptyset:
    - Symbols: $\emptyset, \{\}$
    - Emptyset is a subset of any other set.

## Equality of Equivalency
- Equality: $A=B$
  - All members of $A$ adnd $B$ are the same
  - Both $A\subseteq B$ and $B\subseteq A$ are true.
  - Example: 
    - $A$ is integers between $1$ and $9$
    - $B$ is naural numbers between $1$ and $9$

- Equivalancy ($A\equiv B$) means $n(A)=n(B)$
  - Example: $A=\{x: x\text{ is even}\}$ and $B=\{x: x\text{ is odd}\}$
    - $A\equiv B$

## Examples: Notations

1. Roster: $A = \{2, 4, 6, 8\}$; describe set $A$.

2. Set-builder: 
    - $A = \{x | x \text{ is a multiple of 2 and } 1<x<9\}$
      - Roster notation of $A$:
     
    - $B = \{t | t \text{ is a rational number greater than } 1\}$
      - more algebraic based set-builder for $B$: 

## Examples: Membership and Subsets
:::{.nonincremental}

- $A = \{x | x \text{ is a multiple of 2 and } 1<x<9\}$
- $B = \{t | t \text{ is a rational number greater than } 1\}$

### Symbols:

::: {.columns}
::: {.column}
- $4$ `r hideText('$\\in$')` $A$, 
- $5$ `r hideText('$\\notin$')` $A$,
:::
::: {.column}
- $1/2$ `r hideText('$\\notin$')` $B$,
- $3.53$ `r hideText('$\\in$')` $B$ 
:::
:::
:::
<!-- end columns -->

:::{.fragment .nonincremental}
### Set
- Set of positive integers less than 1: 
:::

## Practice Problems

1. Express the set of even numbers < 10 using roster notation.

\

2. Use set-builder notation for integers greater than 5.


## Q1. 

:::{.nonincremental}

- What does the symbol ∅ mean?
  A) Belongs to
  B) Subset
  C) Empty set
  D) Greater than

:::

## Q2.

:::{.nonincremental}

- What is a correct roster notation for the set of odd numbers < 10?
  A) {1, 2, 3, 4, 5}
  B) {2, 4, 6, 8}
  C) {1, 3, 5, 7, 9}
  D) {0, 2, 4, 6, 8}

:::

## Q3.
:::{.nonincremental}
- Are set of odds less than 10 equivalant to set of evens less than 10?
  a. Yes
  b. No
:::