---
title: "A. Set Theory: Application of Venn Diagram"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-F"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
  showDetails: false
---

### Concept Overview

* A **Venn diagram** shows how events overlap.
* A **contingency table** focuses on each disjoint subset (a.k.a. **outcome**).
* A **tree diagram** builds **outcomes** through the sequences of events or choices.
* All these tools represent **sets of sets**.

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

showDetails <- isTRUE(params$showDetails)
hideText <- function(text, show=showDetails){
  if(show) text else
    funs2teach::hideText(text, docType = 'html')
}

options(knitr.kable.NA = '')
set.seed(123)
```

### Guided Example

1. In a gym of 80 members: 45 do yoga, 35 do weights, 20 do both

   * Build a *Venn Diagram*, a *Contingency Table*, and a *Tree Diagram*.  Tree diagram shows 4 outcomes:

```{r, fig.width=8, fig.height=3, warning=FALSE, message=FALSE}
ggplot()+
  xlim(c(-.2, 5))+
  ylim(c(0, 1))+
  geom_rect(aes(xmin=-0.1, xmax=1.1, ymin=0, ymax=1),
            fill='white', color='black')+
  geom_polygon(aes(x,y), 
               data = funs2teach::circle(c(0.35, .5), .3, n=100),
             color='red', fill='#ffffff00') +
  geom_polygon(aes(x,y), 
               data = funs2teach::circle(c(0.65, .5), .3, n=100),
             color='blue', fill='#ffffff00') +
  ggpp::annotate(geom = 'table', x = 1.2, y = 0.25, size = 4.5,
           label = data.frame(Yoga=c('Yes', 'No'), 
                        `Weight: Yes`=c('', ''), 
                        `Weight: No`=c('', ''), 
                        check.names = FALSE)) +
  geom_segment(aes(x = 3.5, y = 0.5, xend = 4.0, yend = 0.75)) +
  geom_segment(aes(x = 3.5, y = 0.5, xend = 4.0, yend = 0.25)) +
  geom_segment(aes(x = 4.4, y = 0.25, xend = 4.9, yend = 0.35)) +
  geom_segment(aes(x = 4.4, y = 0.25, xend = 4.9, yend = 0.15)) +
  geom_segment(aes(x = 4.4, y = 0.75, xend = 4.9, yend = 0.85)) +
  geom_segment(aes(x = 4.4, y = 0.75, xend = 4.9, yend = 0.65)) +
  coord_fixed() +
  theme_void()

```


### Practice Problem 1
You flip a coin and then roll a die. How many total outcomes?
   * Draw a tree and count outcomes.

\

### Practice Problem 2
A class has 3 math students, 2 art students, and one student takes both. One is picked at random. Answer these questions given we have 6 students in total. 

	– What is the chance the student is in math?


	– What is the chance a randomly chosen student is in math only?

### Quiz: Q1

If you flip a coin twice, how many possible outcomes are there?

* A. 2
* B. 3
* C. 4
* D. 5


### Quiz: Q2
Which statement is true about tree diagrams?

* A. They only apply to numbers
* B. They show possible outcomes of sequential events
* C. They replace Venn diagrams
* D. They require set notation
