---
title: "A. Set Theory"
author: "Mansour Abdoli, PhD"
format:
  live-revealjs:
    slide-number: true
    incremental: true
    chalkboard:
        buttons: true  # Shows icons for easy access
    preview-links: true
    code-overflow: wrap
    footer: "A.Set Theory-A"
#resources:
#  - assets/webr_helpers.R
engine: knitr
execute:
  echo: true
  warning: false
  message: false
#output-files: CK-chx.x-y.y.html
params:
  load_helper: false
---

## Topics:
- Naming Objects
- Set: Naming Type of Objects
- Set as an Object: Set of Sets

{{< include ./_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
#| echo: false
#| output: false
#| warning: false
#| message: false

#  Packages available in your WebR build -

# Load your helper functions (optional)
if(isTRUE(params$load_helper)){
  helpers <- readLines("assets/webr_helpers.R", warn = FALSE)
  eval(parse(text = helpers))
}

options(digits = 3)

```

```{r, echo=FALSE}
#| echo: false
# Helper function
# suppressPackageStartupMessages({
# })

# if(isTRUE(params$load_helper)){
#   source('assets/webr_helpers.R')
# }
# add any helper functions needed

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# suppressPackageStartupMessages({
# })

options(knitr.kable.NA = '')
set.seed(123)
```

## Naming and Grouping Objects
* Naming Objects/Subjects

\

* Grouping Objects/Subjects: Sets.

\

* Describing sets: by listing, using words, or symbols

\

## Guided Examples: Objects/Subjects: 
::: {.columns}
::: {.column}
* Students (Name or Student ID), 

\

* Cars (makes/model), ... 

:::
::: {.column}
* Colors (red, purple, ...)

\
\

* English alphabet
:::
:::
<!-- end columns -->
  
## Guided Examples: Grouping Objects/Subjects:
::: {.columns}
::: {.column}
* Primary Colors:
  * {red, blue, yellow}

\

* Vowels in alphabet:
  * {a, e, i, o, u}
  
:::
::: {.column}
* Math-A100 Students

\
\

* Hybrid Cars
  
\


:::
:::
<!-- end columns -->

## Guided Examples: Sets of Sets
::: {.columns}
::: {.column}
* Colors:
  * {Primary, Secondary, Tertiary, ...}

\

* Cars' Enging Type:
  * {Diesel, Electric, Gas, Hybric, Hydrogen Cell}
:::
::: {.column}
* English alphabet:
  * {Consonants, Vowels}

\
\

* Students:
  * {First Year, Second Year, 3rd Year, 4th Year}

:::
:::
<!-- end columns -->

## Practice Problems

::: {.columns}
::: {.column}
1. List the set of weekdays.

\

:::
::: {.column}
2. List a set of 5 animals you know.

\
:::
:::
<!-- end columns -->

## Q1:

::: {.nonincremental}
* Which of the following is a correct set?
  A) 2 + 3 = 5

  B) {pen, pencil, marker}
  
  C) Red and blue
  
  D) Circle
:::

## Q2:

::: {.nonincremental}
- Which set describes odd numbers less than 10?
  A) {1, 3, 5, 7, 9}
  B) {2, 4, 6, 8, 10}
  C) {3, 6, 9, 12}
  D) {1, 2, 3, 4}
::::